---
title: "annotating_AFL_grounds"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{annotating_AFL_grounds}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The package can create annotations for AFL grounds, with common ground dimensions provided as part of the package. 

```{r setup}
library(AusSportGrounds)
library(ggplot2)
```

## Basic Usage
Since the functions are implemeneted as  `ggplot` layers, it is simple to build a ground. You only have to provide some dimensions that define the `length` and `width` of the ground. 

```{r}
# Create basic AFL field
dim <- list(length = 160,
            width = 140)

ggplot() +
     annotate_afl_oval(dim)

```

There are also some built in dimensions for common grounds such as `ground_mcg`.  

```{r}
ggplot() +
     annotate_afl_oval(ground_mcg)
```

You can also customise the origin for the co-ordinate system. By default, `x = 0` will co-incide with the left-boundary and `y = 0` will be the bottom goal-square. In this sense, the origin is in the bottom left (outside of the actual field of play). You could change this so that the origin was the middle of the ground. 

```{r}
origin <- list(x = -ground_mcg$width/2, y = -ground_mcg$length/2)
ggplot() +
  annotate_afl_oval(ground_mcg, origin = origin) 
```


You can use the built in `theme_ground` to remove all of the ggplot axis to make a clean chart. 

```{r}
# Add blank theme
ggplot() +
  annotate_afl_oval(ground_mcg) +
  theme_ground()

```


## Customising the look and feel

Any valid ggplot theme element can also be passed into `annotate_afl_oval`. Here we can provide a background with the `fill` argument. 

```{r}
# Create the Gabba
ggplot() +
annotate_afl_oval(dim = ground_gabba, colour = "white", fill = "#2ecc71") +
theme_ground()
```

You could also flip the co-ordinates.

```{r}
# Create the Gabba
ggplot() +
annotate_afl_oval(dim = ground_gabba, colour = "white", fill = "#2ecc71") +
theme_ground() +
  coord_flip()

```
## Adding data

Depending on the data you have, you may need to transform it into the right coordinate system (or adjust the 'origin' argument). For simplicity sake, let's assume we don't have to do that. 

Here we take some position data and plot it as points on our oval. 

```{r}
dat <- data.frame(x = c(90, 85, 82, 78, 83, 74, 94, 91),
                  y = c(43, 40, 52, 56, 44, 71, 60, 54))

# Create the Gabba
ggplot() +
  annotate_afl_oval(dim = ground_gabba, colour = "white", fill = "#2ecc71") +
  geom_point(data = dat, aes(x = x, y = y), colour = "black") +
  theme_ground() 

# Need to fix issue with data causing fill to misbehave
```
